Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-04 neurips-20/cvx-flats.tex
S1 changed a sentence to one of Bo's suggestions

Our results make two contributions toward closing this gap.
First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all of the\btw{Bo: changed ``all four'' to ``all of the'' since I think it's not clear what the four are yet} settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
As indirect elicitation is more tractable than calibration, and applies more generally, this observation suggests indirect elicitation as the better choice to study lower bounds on the prediction dimension of a consistent surrogate.
Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all four\botodo{Again we mention the four settings, but we haven't said what they are. probably should either say it explicitly, or change this to something like ``all the above settings''} settings, yielding to our knowledge the most general such bound.
\btw{Bo: added these last two sentences}
A caveat to these results is that, unlike \citet{ramaswamy2016convex}, we generally require surrogates to be ``minimizable'', i.e. functions that attain their global infimum.
Removing this requirement is a technically interesting and perhaps useful direction for future work.

>>>>

Our results make two contributions toward closing this gap.
First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all of the\btw{Bo: changed ``all four'' to ``all of the'' since I think it's not clear what the four are yet} settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
As indirect elicitation is more tractable than calibration, and applies more generally, this observation suggests indirect elicitation as the better choice to study lower bounds on the prediction dimension of a consistent surrogate.
Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all of the above \botodo{Again we mention the four settings, but we haven't said what they are. probably should either say it explicitly, or change this to something like ``all the above settings''} settings, yielding to our knowledge the most general such bound.
\btw{Bo: added these last two sentences}
A caveat to these results is that, unlike \citet{ramaswamy2016convex}, we generally require surrogates to be ``minimizable'', i.e. functions that attain their global infimum.
Removing this requirement is a technically interesting and perhaps useful direction for future work.
